---
title: "TidyTemplate"
date: 2023-02-25
output: html_document
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(tidytext)

library(devtools)
#devtools::install_github('cttobin/ggthemr')
ggthemr::ggthemr('dust')


#theme_set(theme_minimal())
```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2023-02-21")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```
# Cleaning
```{r Cleaning}
bob_ross_raw <- tt$bob_ross
View(bob_ross_raw)

bob_ross <- select(bob_ross_raw, -1)
View(bob_ross)

bob_ross <- bob_ross |> 
  mutate(
    across(Black_Gesso:Alizarin_Crimson, as.logical)
  )

head(bob_ross, 10)
```
```{r}
str(bob_ross_raw)
```

# EDA

## Did Bob Ross paint the same amount of pictures per season?
```{r}
paintings_per_season <- bob_ross %>% 
  group_by(season) %>% 
  summarise(count = n())

paintings_per_season %>% 
  ggplot(aes(x = season, y = count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Number of Paintings per Season by Bob Ross",
       x = "Season",
       y = "# paintings") +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 16, hjust = .5, face = "bold"))
```
## The distribution of Unique colours used by him in his paintings
```{r}
bob_ross %>% ggplot(aes(x = num_colors)) +
  geom_histogram(binwidth = 1, fill = "steelblue", color = "#e9ecef") +
  labs(x = "Number of Unique Colors", y = "Frequency", 
       title = "Distribution of Unique Colors in Bob Ross' Paintings")+
  theme(
    axis.text = element_text(size = 12),
      axis.title = element_text(size = 14),
      plot.title = element_text(size = 16, hjust = .5, face = "bold"))
```

## Which colors were most commonly used each season?
```{r}
bob_ross2 <- select(bob_ross, -c(1,2,5,6,8))
colors_season <- bob_ross2 %>% 
  select(season, contains("_")) %>% 
  pivot_longer(cols = -season, names_to = "color", values_to = "used") %>% 
  mutate(color = str_remove(color, "_"))

freq_table <- colors_season %>% 
  group_by(season, color) %>% 
  summarise(count = sum(used)) %>% 
  ungroup()

freq_table %>% 
  ggplot(aes(x = color, y = season, fill = count)) + 
  geom_tile() +
  labs(x = "Color", y = "Season", fill = "Frequency",
       title = "Frequency of use of each colour per season") +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 16, hjust = .5,face = "bold"),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```
```{r}
word_count <- bob_ross %>% 
  mutate(painting_title = str_to_lower(painting_title)) %>% 
  unnest_tokens(word, painting_title) %>% 
  count(word, sort = TRUE)

# plot top 10 most frequent words

data(stop_words)

word_count <- word_count %>%
  anti_join(stop_words)

word_count %>% 
  top_n(10) %>% 
  ggplot(aes(x = fct_reorder(word, n), y = n)) +
  geom_col(fill = "steelblue", alpha = 0.7) +
  xlab("Words") +
  ylab("Frequency") +
  ggtitle("Top 10 Most Common Words in Painting Titles") +
  coord_flip() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 16, hjust = .5, face = "bold"),
  )
```




# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
